Figures

### 2019-04-16 code/figures.rmd

I2 <- ggplot(res2, aes(x = r, y = I2)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  coord_cartesian(ylim = c(0, 100)) +
  geom_text(x = 0.14, y = Inf, vjust = 7, fontface = "italic", size = 3.5, label = paste0("b = ", format(round(I2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(I2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(italic(I)^2," index"))) +
  scale_x_continuous(name = expression(paste("Biserial correlation ", italic(r))))

H2 <- ggplot(res2, aes(x = r, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  geom_text(x = 0.14, y = Inf, vjust = 7, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(italic(H)^2," index", sep = ""))) +
  scale_x_continuous(name = expression(paste("Biserial correlation ", italic(r))))

@@

```{r r_vs_tau2, fig.asp = 0.618, cache = TRUE}
r_tau2 <- ggplot(res2, aes(x = r, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  geom_text(x = 0.14, y = Inf, vjust = 7, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
  scale_x_continuous(name = expression(paste("Biserial correlation ", italic(r))))

@@

tau2_per_type <- dat %>% #This is to add the effect_type names
  select(effect, effect_type) %>% 
  distinct() %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "Standardized Mean Difference",
                              'Raw mean difference' = "Mean Difference",
                              'Risk difference' = "Risk Difference",
                              'r' = "Correlation")) %>% 
  left_join(tau2_per_type) %>% 
  mutate(eff_size = abs(eff_size)) #need the absolute values for plotting

@@

dens_tau2 <- readRDS("../data/biserial_simulation_results.RDS")
names(dens_tau2) <-  sort(unique(dat$effect))

#Simulated data at various heterogeneity levels, prep for plotting
tau2_dist <- dens_tau2 %>% 
  bind_rows(.id = "effect") %>% 
  rename(Heterogeneity = tau_index) %>% 
  mutate(Heterogeneity = recode(Heterogeneity,
                            '1' = "Zero",
                            '2' = "Small",
                            '3' = "Medium",
                            '4' = "Large"),
         Heterogeneity = as.factor(Heterogeneity))

#Observed tau22 estimates, i.e, results from main table, see table.rmd
#Effects estimated with sourced function 'summarizer'
observed <- dat %>% 
  split(.$effect) %>%  
  map_dfr(summarizer, .id = "effect") %>% 
  select(effect, tau2 = tau2) %>%
  mutate(Heterogeneity = "Observed")

tau2_plot <- ggplot(tau2_dist, aes(x = tau2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
  geom_density(alpha = 0.3) +
  theme_classic() +
  coord_cartesian(xlim = c(0, 100))  +
  scale_fill_brewer(palette = "Dark2",
                    breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                    labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
                        breaks = c("Zero", "Small", "Medium", "Large", "Observed"), 
                        labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_color_brewer(palette = "Dark2", 
                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  theme(legend.position = c(0.85, 0.71),
        legend.background = element_rect(linetype = "solid", color = "black")) +
  scale_y_continuous(name = "Density") +
  scale_x_continuous(name = expression(paste(italic(tau)^2," index", sep = ""))) +
  guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))

#ggsave("../figures/density-tau2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())

#3) combine I2-tau2-density-plots----

densities <- plot_grid(I2_plot, tau2_plot, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
densities
#save_plot("../figures/densities_het.png", densities,
#          nrow = 2, base_height = 5, base_width = 5, dpi = 600)

>>>>

I2 <- ggplot(res2, aes(x = r, y = I2)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  coord_cartesian(ylim = c(0, 100)) +
  geom_text(x = 0.14, y = Inf, vjust = 7, fontface = "italic", size = 3.5, label = paste0("b = ", format(round(I2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(I2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(italic(I)^2," index"))) +
  scale_x_continuous(name = expression(paste("Biserial and pearson correlations ")))

H2 <- ggplot(res2, aes(x = r, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  geom_text(x = 0.14, y = Inf, vjust = 7, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(italic(H)^2," index", sep = ""))) +
  scale_x_continuous(name = expression(paste("Biserial and pearson correlations ")))

@@

```{r r_vs_tau2, fig.asp = 0.618, cache = TRUE}
r_tau2 <- ggplot(res2, aes(x = r, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  geom_text(x = 0.14, y = Inf, vjust = 7, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
  scale_x_continuous(name = expression(paste("Biserial and pearson correlations ")))

@@

#effects that were transformed from OR to SMD
OR2d <- c('Allowed vs. forbidden', 'Gain vs. loss framing', #originally transformed to SMD
           'Norm of reciprocity', 'Low vs. high category scales') #refit as OR

OR_fit <- function(x){ #fit rma to odds raios
  fit <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, n1i = ntreatment, n2i = ncontrol,  data = x)
  hetero <- confint(fit)$random[c(1, 3), ] 
  data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3])}

fit_OR <- dat %>% 
  filter(effect %in% OR2d) %>% 
  split(.$effect) %>% 
  map_dfr(OR_fit, .id = "effect")

tau2_per_type <- dat %>% #This is to add the effect_type names
  select(effect, effect_type) %>% 
  distinct() %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "Standardized Mean Difference",
                              'Raw mean difference' = "Mean Difference",
                              'Risk difference' = "Risk Difference",
                              'r' = "Correlation")) %>% 
  left_join(tau2_per_type) %>% 
  filter(!effect %in% OR2d) %>% #drop old SMD converted OR
  bind_rows(fit_OR) %>% #and instead add OR meta-analyzed as OR
  mutate(effect_type = ifelse(is.na(effect_type), "Odds Ratio", effect_type),
         eff_size = abs(eff_size)) #need the absolute values for plotting

@@

# dens_tau2 <- readRDS("../data/biserial_simulation_results.RDS")
# names(dens_tau2) <-  sort(unique(dat$effect))
# 
# #Simulated data at various heterogeneity levels, prep for plotting
# tau2_dist <- dens_tau2 %>% 
#   bind_rows(.id = "effect") %>% 
#   rename(Heterogeneity = tau_index) %>% 
#   mutate(Heterogeneity = recode(Heterogeneity,
#                             '1' = "Zero",
#                             '2' = "Small",
#                             '3' = "Medium",
#                             '4' = "Large"),
#          Heterogeneity = as.factor(Heterogeneity))
# 
# #Observed tau22 estimates, i.e, results from main table, see table.rmd
# #Effects estimated with sourced function 'summarizer'
# observed <- dat %>% 
#   split(.$effect) %>%  
#   map_dfr(summarizer, .id = "effect") %>% 
#   select(effect, tau2 = tau2) %>%
#   mutate(Heterogeneity = "Observed")
# 
# tau2_plot <- ggplot(tau2_dist, aes(x = tau2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
#   geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
#   geom_density(alpha = 0.3) +
#   theme_classic() +
#   coord_cartesian(xlim = c(0, 100))  +
#   scale_fill_brewer(palette = "Dark2",
#                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
#                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
#   scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
#                         breaks = c("Zero", "Small", "Medium", "Large", "Observed"), 
#                         labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
#   scale_color_brewer(palette = "Dark2", 
#                      breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
#                      labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
#   theme(legend.position = c(0.85, 0.71),
#         legend.background = element_rect(linetype = "solid", color = "black")) +
#   scale_y_continuous(name = "Density") +
#   scale_x_continuous(name = expression(paste(italic(tau)^2," index", sep = ""))) +
#   guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))
# 
# #ggsave("../figures/density-tau2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())
# 
# #3) combine I2-tau2-density-plots----
# 
# densities <- plot_grid(I2_plot, tau2_plot, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
# densities
# #save_plot("../figures/densities_het.png", densities,
# #          nrow = 2, base_height = 5, base_width = 5, dpi = 600)
